---
title: "Make Your Computational Analysis Citable 1"
description: |
  This post introduces the steps needed by academic and non-acadmics to make their computational analysis citable regardless of being published in journals. 
author:
  - name: Batool Almarzouq 
    url:  https://batoolmm.netlify.app/
    affiliation: The University of Liverpool
    affiliation_url: https://www.liverpool.ac.uk/
date: 3-18-2021
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# Learn more about creating blogs with Distill at:
# https://rstudio.github.io/distill/blog.html
```

#### Why make our computational analysis citable?

Although there are overwhelming resources about licensing and citation for R software packages, there's less attention paid to making non-package (data science) code in R citable. Academics and researchers who want to embrace Open Science practices are mostly unaware of how to make their R code citable before publishing in academic journals and what kind of license they may use to protect the intellectual property of their work.

Books and published journal articles have always been supplemented with DOIs (digital object identifiers), a key element in the process of research and academic discourse but there's less attention paid to unpublished computational analysis, which is usually abandoned in GitHub (or in someone's drive).

As a researcher, we often spend long time planning and designing our project, collecting and processing data but we often can't publish all the results and analysis if it deemed uninteresting to the journal reviewers.

-   Reproducibility
-   License
-   Zenodo
-   Publishing throughout the research cycle - Open Science

```{r}
plot(1:10)
```

This is noted [^1]

[^1]: it was meant to builds on other websites

<aside>

This will not just improve reproducibility but also collaboration and transparancy.

</aside>
